A Machine Profile Summary

### 2022-06-14 MachineSummary/MachineSummary.Rmd
Fix boxplots

Note that it appears that the first cycle of the loop is very slow. ?? is this
byte-compiling?

```{r loopesc}
loopesc <- function(nn){
  ss <- 0
  for (i in 1:nn) {
    xx <- exp(sin(cos(1.0*i)))
    ss <- ss + xx
  }
  xx
}

require("microbenchmark")
# nvals<-c(1000, 10000, 100000, 1000000)
# tvals<-rep(NA, length(nvals))
# i<-0
# for (nn in nvals) {
#   i <- i + 1
#   cat(nn, "\n")
  nn <- 10000
  library(compiler)
  le <- cmpfun(loopesc)
  te <- microbenchmark(le(nn), unit='us')
  print(te)
  boxplot(te)
  tt <- microbenchmark(loopesc(nn), unit = 'us')
  print(tt)
  boxplot(tt)
#  ht<-hist(tt$time)
#  plot(ht, main="Histogram of loopesc times")
  tt2 <- microbenchmark(loopesc(nn), unit = 'us', control=list(warmup=2))
  print(tt2)
  boxplot(tt2)

#  ht2<-hist(tt2$time)
#  plot(ht2, main="Histogram of loopesc times after 2 warmup cycles")
# }
# plot(log10(nvals), log(tvals))
```

>>>>

Note that it appears that the first cycle of the loop is very slow. Fortunately 
`microbenchmark` seems aware of this, and we can specify a number of "warmup"
cycles. In the present case, we tried 2 cycles. We also tried byte compiling
the loopesc function with the `compiler` package. Note that rerunning the 
code several times gave slightly different boxplots, but the general characteristics
were preserved.

```{r loopesc, echo=TRUE}
loopesc <- function(nn){
  ss <- 0
  for (i in 1:nn) {
    xx <- exp(sin(cos(1.0*i)))
    ss <- ss + xx
  }
  xx
}
```

```{r looptime, code=readLines("loopbox.R"), echo=FALSE}
```
